Laws for Creating Trust in the Blockchain Age

### 2017-10-13 tex/article.tex
Minor polish

Being the ruler of your own identity is closely related to the core concept of Bitcoin.
Bitcoin creates money without banks, but also provides users with an exceptional level of control.
The novelty of Bitcoin is that is provides a system where nobody can stop a specific entity from spending their money.
Identity autonomy provides a new level of citizen empowerment and enables financial sovereignty.\footcite{matouk2009financial}

@@

Obtaining agreement from numerous parties during several of the stages of property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion and several countries are already exploring the possibilities to store land transferral transactions on a global ledger.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration}\,\footcite{forbeslandtiles}
The importance of transparency that blockchains offer is even more apparent when one considers regions in which public's trust has been damaged, e.g., in war-torn Colombia, and land registration requires the involvement of its citizens.\footcite{landrightscolumbia}

@@

We present a Self-Sovereign Identity (SSI) mechanism, capable of verifying statements, without any central organization, point-of-failure or possibility of data tracking, giving users full control over their identity.
Self-sovereign identity serves a purpose in a large range of applications, have the potential to speed up traditional, inefficient verification processes and enables inter-operability between companies, individuals and governments while respecting the privacy of identity owners.
In a SSI system, civilians, legal entities and objects are able to prove statements such as "my age is at least 18" to others that legally require verification of this claim, like alcoholic shops or car rental services.
A reliable SSI mechanism is an indispensable building block to empower blockchain-based applications and sector-specific processes, operating at higher levels in our technology stack.

@@

To obtain insight in the real-world efficiency of our system, we created an open alternative to the proprietary Uber taxi marketplace.
Uber, one of the largest companies operating in the sharing economy, is a two-sided market where taxi drivers, offering a ride to a location (represented by a sell offer), are matched with users requesting transportation (represented by a buy offer).
Since there is no public, reliable dataset provided by the Uber platform, we use historical information of taxi rides published by the government of New York instead.\footcite{newyorktaxi}
This dataset provides temporal and geographical information of pick-up and drop-off location of each taxi ride.
To explore the limitations of our system, we analysed the dataset and subtracted 1050 offers during the busiest period in 2015, November 1, 00:59:57 to November 1, 01:01:16.
The experiment is executed in real-time on a 42 node cluster of the DAS-5 supercomputer where we assume a total of 550 taxi drivers providing rides and 500 passengers requesting transportation.\footcite{bal2016medium}
To guarantee that every passenger can be matched with a taxi driver, we assume an oversupply of 10\%, this corresponds to the realistic situation where taxi drivers are waiting for new passengers.
During the experiment, each passenger and taxi driver create exactly one buy or sell offer and is connected to at least ten other random taxi drivers (matchmakers) in the network.
The experiment starts by taxi drivers placing ride offers with an interval of 100 milliseconds on our decentralized market.
After all ride offers have been placed, each passenger creates and disseminates a ride request.
In the end, a total of 550 sell offers and 500 buy offers are created.
When a new offer is placed, it is disseminated to other matchmakers who inform the creator of this offer about potential matches.
In our system, a trader does not accept the first incoming match immediately but instead, waits for and aggregates additional matches for a duration of two seconds after which a trader accepts the optimal match and declines the others.
This period should allow a trader to process and store at least 100 incoming matches.
It is also assumed that only taxi drivers perform matching since they are likely to be connected to the network for a longer period of time.
Matching efficiency is measured by the average distance between a passenger and a taxi driver where we aim to minimize this distance.
Taxi drivers and passengers are matched based on their great circle distance.

>>>>

Being the ruler of your own identity is closely related to the core concept of Bitcoin.
Bitcoin creates money without banks, but also provides users with an exceptional level of control.
The novelty of Bitcoin is that it provides a system where nobody can stop a specific entity from spending their money.
Identity autonomy provides a new level of citizen empowerment and enables financial sovereignty.\footcite{matouk2009financial}

@@

Obtaining agreement from numerous parties during the several stages of property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion and several countries are already exploring the possibilities to store land transferral transactions on a global ledger.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration}\,\footcite{forbeslandtiles}
The importance of transparency that blockchains offer is even more apparent when one considers regions in which public's trust has been damaged, e.g., in war-torn Colombia, and land registration requires the involvement of its citizens.\footcite{landrightscolumbia}

@@

We present a Self-Sovereign Identity (SSI) mechanism, capable of verifying statements without the requirement for a centralized authority and void of the possibility of data tracking, giving users full control over their identity.
Self-sovereign identity serves a purpose in a large range of applications, have the potential to speed up traditional, inefficient verification processes and enables inter-operability between companies, individuals and governments while respecting the privacy of identity owners.
In a SSI system, civilians, legal entities and objects are able to prove statements such as "my age is at least 18" to others that legally require verification of this claim, like alcoholic shops or car rental services.
A reliable SSI mechanism is an indispensable building block to empower blockchain-based applications and sector-specific processes, operating at higher levels in our technology stack.

@@

To obtain insight in the real-world efficiency of our system, we created an open alternative to the proprietary Uber taxi marketplace.
Uber, one of the largest companies operating in the sharing economy, is a two-sided market where taxi drivers, offering a ride to a location (represented by a sell offer), are matched with users requesting transportation (represented by a buy offer).
Since there is no public, reliable dataset provided by the Uber platform, we use historical information of taxi rides published by the government of New York instead.\footcite{newyorktaxi}
This dataset provides temporal and geographical information of pick-up and drop-off location of each taxi ride.
To explore the limitations of our system, we analysed the dataset and subtracted 1050 offers during the busiest period in 2015, November 1, 00:59:57 to November 1, 01:01:16.
The experiment is executed in real-time on a 42 node cluster of the DAS-5 supercomputer where we assume a total of 550 taxi drivers providing rides and 500 passengers requesting transportation.\footcite{bal2016medium}
To guarantee that every passenger can be matched with a taxi driver, we assume an oversupply of 10\%, this corresponds to the realistic situation where taxi drivers are waiting for new passengers.
During the experiment, each passenger and taxi driver create exactly one buy or sell offer and is connected to at least ten other random taxi drivers (matchmakers) in the network.
The experiment starts by taxi drivers placing ride offers with an interval of 100 milliseconds on our decentralized market.
After all ride offers have been placed, each passenger creates and disseminates a ride request.
In the end, a total of 550 sell offers and 500 buy offers are created.
When a new offer is placed, it is disseminated to other matchmakers who inform the creator of this offer about potential matches.
In our system, a trader does not accept the first incoming match immediately but instead, waits for and aggregates additional matches for a duration of two seconds after which a trader accepts the optimal match and declines the others.
This period should allow a trader to process and store at least 100 incoming matches.
It is also assumed that only taxi drivers perform matching since they are likely to be connected to the network for a longer period of time.
Matching efficiency is measured by the average distance between a passenger and a taxi driver where we aim to minimize this distance.
Taxi drivers and passengers are matched based on their distance as the crow flies.
